Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-09-15 manuscript/manuscript.tex
corrected references in discussion

Finally, the intersection of data curation and machine learning for
public policy applications opens new avenues for improving governance.
High-quality data enables machine learning models to better predict
trends, allocate resources, and address service delivery issues, such
as delays in responding to 311 complaints. The COVID-19 pandemic
underscored the importance of real-time, trustworthy data in crisis
management, where the accuracy and timeliness of data-driven insights
were critical for public health responses. Without proper data
curation, machine learning models used during the pandemic would have
been compromised, affecting decisions on resource allocation and
service provision \citep{wu2020subnational, kumar2020machine}.
Future efforts could focus on automating data curation processes,
particularly in real-time data pipelines, to ensure that the data used
in machine learning models remains accurate, clean, and reliable
\citep{chu2016data, zhang2019automating}.

>>>>

Finally, the intersection of data curation and machine learning for
public policy applications opens new avenues for improving governance.
High-quality data enables machine learning models to better predict
trends, allocate resources, and address service delivery issues, such
as delays in responding to 311 complaints. The COVID-19 pandemic
underscored the importance of real-time, trustworthy data in crisis
management, where the accuracy and timeliness of data-driven insights
were critical for public health responses. Without proper data
curation, machine learning models used during the pandemic would have
been compromised, affecting decisions on resource allocation and
service provision \citep{worby2020face, khemasuwan2021applications}.
Future efforts could focus on automating data curation processes,
particularly in real-time data pipelines, to ensure that the data used
in machine learning models remains accurate, clean, and reliable
\citep{chu2016data, hurbean2021open}.
